{\bf {\Large Title....}}

### 2016-06-29 ident_manu.Rnw
sensitivity tables done

\begin{equation}
L1 = \sum|S_{ij}|/n
\end{equation}
\begin{equation}
L2 = \sqrt{\sum\left(S_{ij}^2\right)|/n}
\end{equation}

@@

@@

<<optsens, eval = T>>=

data(sens_ests)
data(sens_ests_cat)

categ <- 'Optics'

labs <- parcats2()[[categ]] %>% 
  data.frame %>% 
  rename(Parameter = shrt)

totab <- filter(sens_ests_cat, Category %in% categ) %>% 
  select(Parameter) %>% 
  left_join(., sens_ests$sens, by = 'Parameter') %>% 
  left_join(., labs, by = 'Parameter') %>% 
  select(Parameter, lngs, vals, L1, L2) %>% 
  arrange(-L1) %>% 
  mutate(
    Parameter = paste0('\\textit{', gsub('_[0-9]$', '', Parameter), '}'),
    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
    lngs = gsub('_', '\\\\_', lngs), 
    L1 = sapply(L1, scinot), 
    L2 = sapply(L2, scinot)
  ) %>% 
  rename(
    Description = lngs, 
    Value = vals
  )

# final table formatting
Parameter <- totab$Parameter
totab <- totab[,-1]
cap.val<-'Test'

latex( 
  totab,
  file = '',
  rowlabel = 'Parameter',
  caption = cap.val,
  caption.loc = 'top',
  # rgroup = segs,
  # n.rgroup = c(1, rep(4, 2)),
#   cgroup = vars,
#   n.cgroup = c(2, 2),
  rowname = Parameter,
  label = 'tab:optsens'
  )

@

>>>>

\begin{equation} \label{l1}
L1 = \sum|S_{ij}|/n
\end{equation}
\begin{equation} \label{l2}
L2 = \sqrt{\sum\left(S_{ij}^2\right)|/n}
\end{equation}

@@

\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}

@@

<<optsens, eval = T, cache = F>>=
senstab1('Optics', 'optsens')
@

<<tempsens, eval = T, cache = F >>=
senstab2('Temperature', 'tempsens')
@

<<phytosens, eval = T, cache = F>>=
# data(sens_ests_cat)
# tmp <- filter(sens_ests_cat, Category == 'Phytoplankton')
# quantile(tmp$error)
senstab2('Phytoplankton', 'phytosens', sub = 0.59, sub.txt = 'Parameters less than the 75\\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.')
@

<<zoopsens, eval = T, cache = F>>=
senstab2('Zooplankton', 'zoopsens')
@

<<omsens, eval = T, cache = F>>=
senstab1('Organic Matter', 'omsens')
@

### 2016-06-29 ident_manu.tex
sensitivity tables done

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Jun 28 11:58:04 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

%latex.default(totab, file = "", rowlabel = "Parameter", caption = cap.val,     caption.loc = "top", rowname = Parameter, label = "tab:optsens")%
\begin{table}[!tbp]
\caption{Test\label{tab:optsens}} 
\begin{center}
\begin{tabular}{llrll}
\hline\hline
\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Description}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
\textit{astar490}&Chla specific absorption at 490 nm&$0.0375$&$1.64$&$8.64$\tabularnewline
\textit{astarOMA}&OM\_A specific absorption at 490 nm&$0.1000$&$2.29\times 10^{-2}$&$9.52\times 10^{-2}$\tabularnewline
\textit{astarOMZ}&OM\_Z specific absorption at 490 nm&$0.1000$&$5.65\times 10^{-3}$&$1.42\times 10^{-2}$\tabularnewline
\textit{Kcdom}&AOP, light attenuation due to CDOM&$0.0010$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
\hline
\end{tabular}\end{center}

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Jun 29 09:01:37 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of optics parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.\label{tab:optsens}} 
\begin{center}
\begin{tabular}{lllll}
\hline\hline
\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$1.64$&$8.64$\tabularnewline
OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$&$0.1$\tabularnewline
OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$0.01$&$0.01$\tabularnewline
AOP, light attenuation due to CDOM&\textit{Kcdom}&$0$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
\hline
\end{tabular}\end{center}}

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{Optimum temperature for growth(C)}&&&\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{P4}$}&$17$&$2.9$&$22.95$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{Z2}$}&$26$&$0.18$&$2.59$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{P5}$}&$26$&$0.17$&$0.72$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{P2}$}&$22$&$0.16$&$0.82$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{Z1}$}&$22$&$0.16$&$0.33$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{P3}$}&$17$&$0.14$&$0.78$\tabularnewline
~~\textit{Tref(nospA+nospZ)$_{P1}$}&$22$&$0.12$&$0.29$\tabularnewline
\hline
\end{tabular}\end{center}}

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of phytoplankton parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter. Parameters less than the 75\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.\label{tab:phytosens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{coefficient for non-limiting nutrient}&&&\tabularnewline
~~\textit{aN$_{P1}$}&$1$&$2.7$&$47.26$\tabularnewline
~~\textit{aN$_{P3}$}&$1$&$0.66$&$3.16$\tabularnewline
\hline
{half-saturation constant for N}&&&\tabularnewline
~~\textit{Kn$_{P3}$}&$5.93$&$1.15$&$9.22$\tabularnewline
~~\textit{Kn$_{P4}$}&$1.13$&$0.62$&$2.5$\tabularnewline
\hline
{initial slope of the photosynthesis-irradiance relationship}&&&\tabularnewline
~~\textit{alpha$_{P4}$}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
~~\textit{alpha$_{P3}$}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
~~\textit{alpha$_{P5}$}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
\hline
{minimum N cell-quota}&&&\tabularnewline
~~\textit{QminN$_{P3}$}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
~~\textit{QminN$_{P4}$}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
~~\textit{QminN$_{P1}$}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
\hline
{mortality coefficient}&&&\tabularnewline
~~\textit{mA$_{P3}$}&$0.03$&$2.98$&$14.34$\tabularnewline
~~\textit{mA$_{P4}$}&$0.11$&$1.35$&$7.04$\tabularnewline
\hline
{N-uptake rate measured at umax}&&&\tabularnewline
~~\textit{vmaxN$_{P5}$}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
~~\textit{vmaxN$_{P4}$}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
~~\textit{vmaxN$_{P3}$}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
~~\textit{vmaxN$_{P1}$}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
\hline
{P-uptake rate measured at umax}&&&\tabularnewline
~~\textit{vmaxP$_{P3}$}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
~~\textit{vmaxP$_{P1}$}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
\hline
{phytoplankton basal respiration coefficient}&&&\tabularnewline
~~\textit{respb$_{P4}$}&$0.02$&$3.1$&$26.48$\tabularnewline
~~\textit{respb$_{P3}$}&$0.02$&$2.15$&$6.35$\tabularnewline
~~\textit{respb$_{P5}$}&$0.02$&$0.81$&$8.61$\tabularnewline
\hline
{phytoplankton carbon/cell}&&&\tabularnewline
~~\textit{Qc$_{P1}$}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
~~\textit{Qc$_{P3}$}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
~~\textit{Qc$_{P2}$}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
~~\textit{Qc$_{P4}$}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
\hline
{phytoplankton growth respiration coefficient}&&&\tabularnewline
~~\textit{respg$_{P4}$}&$0.1$&$0.98$&$7.37$\tabularnewline
\hline
\end{tabular}\end{center}}

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of zooplankton parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:zoopsens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{assimilation efficiency as a fraction of ingestion}&&&\tabularnewline
~~\textit{Zeffic$_{P1}$}&$0.4$&$0.23$&$0.55$\tabularnewline
~~\textit{Zeffic$_{P2}$}&$0.4$&$0.21$&$0.75$\tabularnewline
\hline
{half saturation coefficient for grazing}&&&\tabularnewline
~~\textit{ZKa$_{P1}$}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
~~\textit{ZKa$_{P2}$}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
\hline
{maximum growth rate of zooplankton}&&&\tabularnewline
~~\textit{Zumax$_{P2}$}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
~~\textit{Zumax$_{P1}$}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
\hline
{proportion of grazed phytoplankton lost to sloppy feeding}&&&\tabularnewline
~~\textit{Zslop$_{P1}$}&$0.25$&$0.12$&$0.33$\tabularnewline
\hline
{Zooplankton biomass-dependent respiration factor}&&&\tabularnewline
~~\textit{Zrespb$_{P1}$}&$0.1$&$0.45$&$3.02$\tabularnewline
~~\textit{Zrespb$_{P2}$}&$0.42$&$0.09$&$1.05$\tabularnewline
\hline
{zooplankton carbon/individual}&&&\tabularnewline
~~\textit{ZQc$_{P2}$}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
~~\textit{ZQc$_{P1}$}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
\hline
{Zooplankton growth-dependent respiration factor}&&&\tabularnewline
~~\textit{Zrespg$_{P1}$}&$0.2$&$0.24$&$3.19$\tabularnewline
~~\textit{Zrespg$_{P2}$}&$0.3$&$0.12$&$0.31$\tabularnewline
\hline
{Zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
~~\textit{Zm$_{P2}$}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
~~\textit{Zm$_{P1}$}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
\hline
{zooplankton nitrogen/individual}&&&\tabularnewline
~~\textit{ZQn$_{P1}$}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
~~\textit{ZQn$_{P2}$}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
\hline
{zooplankton phosphorus/individual}&&&\tabularnewline
~~\textit{ZQp$_{P2}$}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
~~\textit{ZQp$_{P1}$}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
\hline
\end{tabular}\end{center}}

%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of organic matter parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.\label{tab:omsens}} 
\begin{center}
\begin{tabular}{lllll}
\hline\hline
\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
rate constant for nitrification&\textit{k11}&$5$&$2.11$&$16.1$\tabularnewline
O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.91$&$11.76$\tabularnewline
turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.49$&$6.83$\tabularnewline
turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.37$&$3.46$\tabularnewline
half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.24$&$7.98$\tabularnewline
half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.56$&$1.92$\tabularnewline
decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.01$&$0.03$\tabularnewline
\hline
\end{tabular}\end{center}}
